Interactive Visualization of Hierarchically Structured Data

### 2016-12-07 treelapse.Rmd
Fix reference to bike sankey

```{r bikesankey, fig.cap = "We can interpret the regression tree using an interactive DOI representation."}
knitr::include_graphics("bike_sankey.png")
```

>>>>

```{r bikesankey, fig.cap = "We can interpret the regression tree using an interactive DOI representation."}
knitr::include_graphics("figure/bike_sankey.pdf")
```
